%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Solo} % Role
    {MiniC Editor \href{https://github.com/yanshengjia/nucleon}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {Oct. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built a GUI editor with syntax highlighting feature for MiniC using Python and Qt.}
        \item {Integrated the editor with the MiniC compiler to detect programming errors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Role
    {MiniC Compiler \href{https://github.com/yanshengjia/compiler}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {May. 2016 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented the ``Regular Expression -> NFA'' converter in Python.}
        \item {Implemented the LR(1) parser and relevant semantic analysis in Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Solo} % Role
    {Course Projects of Artificial Intelligence \href{https://github.com/yanshengjia/artificial-intelligence}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {Mar. 2016 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Applied neural networks for face recognition.}
        \item {Implemented genetic algorithm in Matlab to deal with the functional maximum problem.}
        \item {Implemented A* algorithm in C++ to solve the 24 puzzle problem.}
        \item {Implemented QS4 algorithm in C++ to tackle the million queens problem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {Entity Linker \href{https://github.com/acmom/entity-linker}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {Mar. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Did research on and compare multiple entity linking algorithms.}
        \item {Built an EL system that could associate each mention in a Web table with its referent entity in Wikipedia.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Team Leader} % Role
    {My Minecraft \href{https://github.com/seucs/my-minecraft}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {Sep. 2015 - Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Developed a small 3D game similar to Minecraft with OpenGL.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Solo} % Role
  %   {Weibo Crawler \href{https://github.com/yanshengjia/crawler/tree/master/weiboCrawler}{[\underline{Link}]}} % Title
  %   {Nanjing, China} % Location
  %   {Nov. 2015 - Nov. 2015} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s)
  %       \item {Developed a robust multithreaded Web crawler to collect data from Chinese social media Weibo.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Core Member} % Role
    {Virtual Campus \href{https://github.com/acmom/vcampus}{[\underline{Link}]}} % Title
    {Nanjing, China} % Location
    {Sep. 2015 - Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        % \item {Designed databases and developed Data Access Object (DAO) class in Java for Virtual Campus which includes student management module, library module, chat module, logging-in module, online shop module and administration of education module.}
        \item {Developed a Java software that could manage student information.}
        \item {Added additional features, such as online chat, digital library, online store, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
